[dcpo_demsupport]

### 2020-06-27 paper/dcpo_demsupport.Rmd
add ivt_dcpo

# see https://github.com/fsolt/dcpo_article/blob/master/R/validation_table.R for more to add when we have it

>>>>

load(here::here("data", "dcpo_replication_y_r_pred.rda"))

ivt_dcpo <- DCPOtools::internal_validation_tests(dcpo_replication_input, dcpo_replication_y_r_pred)
# see https://github.com/fsolt/dcpo_article/blob/master/R/validation_table.R for more to add when we have it
